---
title: "Plot MSA Spectra"
author: "John Minter"
date: "Created: 2018-02-01 Last Modified: 2018-02-11"
output:
  html_document:
    keep_md: true
    variant: github_md
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load a spectrum

First we get our exemplar **.msa** format spectrum file. I had included
the file in the `rEDS` package. We will suppress the messages where R
has loaded the required packages by using the optional `quietly` 
variable.

```{r}
library(rEDS, quietly=TRUE)
fi <- system.file("extdata", "Benitoite.msa", package = "rEDS")
print(fi)
```

Next, we create a Spectrum object using the `SingleMSA` function.
You can get the help page by typing `??rEDS::singleMSA` into the
R console.

```{r, message=FALSE}
spc <- singleMSA(fi, probecur=2.5)
```

and now we can plot the spectrum.

```{r, fig.width=7}
plot(spc, maxEnergy=10000, doLog=TRUE)
```

We can also create a ggplot with a linear intensity scale. You can
get the help page by typing `??rEDS::ggplotSpectrumLinY` into the 
R console.

```{r, fig.width=7}
plt <- ggplotSpectrumLinY(fi, "Benitoite", 0.2, 7.0, 1.0, 2.5)
print(plt)
```

next we will make a plot with a logarithmic intensity

```{r, fig.width=7}
plt <-ggplotSpectrumLogY(fi, "Benitoite", 0.2, 7.0, 1.0, 2.5)
print(plt)
```
